Codebook
========
Codebook was generated at `r as.character(Sys.time())` after generating the data (script run_analysis.R)

Source of the data
------------------

https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip

Description of the data
-----------------------

http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones

Variable list and descriptions
------------------------------

Variable name    | Description
-----------------|------------
subject          | ID the subject who performed the activity for each window sample. Its range is from 1 to 30.
activity         | Activity name
featDomain       | Feature: Time domain signal or frequency domain signal (Time or Freq)
featInstrument   | Feature: Measuring instrument (Accelerometer or Gyroscope)
featAcceleration | Feature: Acceleration signal (Body or Gravity)
featVariable     | Feature: Variable (Mean or SD)
featJerk         | Feature: Jerk signal
featMagnitude    | Feature: Magnitude of the signals calculated using the Euclidean norm
featAxis         | Feature: 3-axial signals in the X, Y and Z directions (X, Y, or Z)
featCount        | Feature: Count of data points used to compute `average`
featAverage      | Feature: Average of each variable for each activity and each subject

Dataset structure
-----------------

```{r}
str(msSet2)
```

Show a few rows of the dataset
------------------------------

```{r}
head(msSet2)
```

Summary 
-------

```{r}
summary(msSet2)
```
